Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-28 paper/ms.tex
finished section 4

\subsection{Observational constraints on the occupation fraction}

We impose a different restriction using the observational results
by \cite{Hayes2010}. These authors constrained the value of $f_{\rm
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$.

For the cosmological parameters used in this \documentname the age of
the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$
Gyr. We assume that the physical conditions that determine the escape
fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$
remain constant over that time scale. We limits the escape fraction to
be in the range further pick models that have an occupation fraction of $f_{\rm
  occ}\leq 0.2$ to allow for some flexibility. With this additional
constraint between $35$ to $40$ models are consistent with
observations. 
%Considering an occupation fraction $f_{\rm occ}=0.20$
%another $39$This constraint help us to
%select $\sim 10\%$ of theoriginal models that were considered as
%consistent with observations in the previous section.

Figure  \ref{fig:restriction_mock_and_f_occ}   shows the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random}
methods. The list for the parameters in these models is found in the appendix in
Table XX.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
\end{center} 
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. The results for
  the {\texttt random} methodology area very similar to the ones
  presented here for the {\texttt match} method.
  \label{fig:restriction_mock}}  
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
\end{center} 
\caption{Favored models when the constraints on the maximal number of
  consistent mocks and the observational constrain on the occupation
  fraction are included.
  \label{fig:restriction_mock_and_f_occ}}  
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
10.1 & 10.2 & 0.1\\
10.3 & 10.5 & 0.1\\
10.4 & 10.7 & 0.1\\
10.5 & 10.9 & 0.1\\
10.6 & 11.2 & 0.1\\
10.6 & 11.3 & 0.1\\
10.6 & 11.4 & 0.1\\
10.1 & 10.2 & 0.1\\
10.3 & 10.5 & 0.1\\
10.4 & 10.7 & 0.1\\
10.5 & 10.9 & 0.1\\
10.5 & 11.0 & 0.1\\
10.6 & 11.2 & 0.1\\
10.6 & 11.3 & 0.1\\
10.6 & 11.4 & 0.1\\
10.6 & 11.5 & 0.1\\
10.6 & 11.6 & 0.1\\
10.6 & 11.7 & 0.1\\\hline\hline

10.4 & 10.5 & 0.2\\
10.6 & 10.8 & 0.2\\
10.7 & 11.0 & 0.2\\
10.8 & 11.2 & 0.2\\
10.8 & 11.3 & 0.2\\
10.9 & 11.6 & 0.2\\
10.9 & 11.7 & 0.2\\
10.9 & 11.8 & 0.2\\
10.9 & 11.9 & 0.2\\
10.9 & 12.0 & 0.2\\
10.9 & 12.1 & 0.2\\
10.9 & 12.2 & 0.2\\
10.9 & 12.3 & 0.2\\
10.9 & 12.4 & 0.2\\
10.9 & 12.5 & 0.2\\
10.9 & 12.6 & 0.2\\
10.9 & 12.7 & 0.2\\
10.9 & 12.8 & 0.2\\
10.9 & 12.9 & 0.2\\
10.9 & 13.0 & 0.2\\
10.6 & 10.8 & 0.2\\
10.7 & 11.0 & 0.2\\
10.8 & 11.2 & 0.2\\
10.8 & 11.3 & 0.2\\
10.8 & 11.4 & 0.2\\
10.9 & 11.7 & 0.2\\
10.9 & 11.8 & 0.2\\
10.9 & 11.9 & 0.2\\
10.9 & 12.0 & 0.2\\
10.9 & 12.1 & 0.2\\
10.9 & 12.2 & 0.2\\
10.9 & 12.3 & 0.2\\
10.9 & 12.4 & 0.2\\
10.9 & 12.5 & 0.2\\
10.9 & 12.6 & 0.2\\
10.9 & 12.7 & 0.2\\
10.9 & 12.8 & 0.2\\
10.9 & 12.9 & 0.2\\
10.9 & 13.0 & 0.2\\\hline\hline
\end{tabular}
\end{center}
\end{table}

>>>>

\subsection{Additional  Constraints on the Occupation Fraction}

We impose an additional restriction using the observational results
by \cite{Hayes2010}. They constrained the value of $f_{\rm
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.

We limit the occupation fraction to
be in the range 
%further pick models that have an occupation fract
$f_{\rm
  occ}\leq 0.2$ to allow for some flexibility on the time evolution
and the uncertainty in the dust correction used to infer the escape fraction. 
%Considering an occupation fraction $f_{\rm occ}=0.20$
%another $39$This constraint help us to
%select $\sim 10\%$ of theoriginal models that were considered as
%consistent with observations in the previous section. 
Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
With this additional constraint between $35$ to $40$ models are
consistent with observations, this represents a factor of $\sim 2$
reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
excluded and the best models are now clustered around a narrow region
in parameter space. The list for the model parameters is in the
Appendix in Table \ref{table:models_match}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
\end{center} 
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. The results for
  the {\texttt random} methodology (not shown here) are very similar to the ones
  presented here for the {\texttt match} method.
  \label{fig:restriction_mock}}  
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
\end{center} 
\caption{Best models when both the constraints on the maximal number
  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.6& 11.7& 0.1\\
10.6& 10.8& 0.2\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
10.9& 12.0& 0.2\\
10.9& 12.1& 0.2\\
10.9& 12.2& 0.2\\
10.9& 12.3& 0.2\\
10.9& 12.4& 0.2\\
10.9& 12.5& 0.2\\
10.9& 12.6& 0.2\\
10.9& 12.7& 0.2\\
10.9& 12.8& 0.2\\
10.9& 12.9& 0.2\\
10.9& 13.0& 0.2\\\hline\hline
\end{tabular}
\end{center}
\caption{List of model parameters for the best models that have all
  mock surveys consistent with observations and an occupation
  fraction $f_{\rm occ}\leq 0.2$. This corresponds to the {\texttt
    match} method to construct the mock surveys. \label{table:models_match}. }
\end{table}
